---
title: "Simulation 1: matched truth"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulation 1: matched truth}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width = 6,
  fig.height = 4
)
```

This vignette reproduces a small version of "Simulation 1: matched truth"
from Zhang, Ok, and Ni (submitted). It generates counts from LODI's own
generative model and shows that the MCMC recovers the within-time
cross-feature covariance $\Sigma_t = \Lambda\Lambda^\top + \sigma^2_t I_J$
under matched conditions.

Settings are chosen small so the vignette runs in under a minute; larger
runs simply increase `N`, `T`, `J`, and `niter`.

```{r setup}
library(LODI)
set.seed(1)
```

## 1. Simulate a matched-truth dataset

```{r simulate}
sim <- simulate_lodi(
  N = 15, T = 5, J = 20, K = 3,
  phi = 0.8, V = 0.2, rho = 0.7, sigma2 = 0.5,
  seed = 1
)
dim(sim$Y)          # N x T x J
mean(sim$Y == 0)    # simulated zero rate
```

## 2. Fit LODI

Short-run MCMC settings for the vignette; production runs typically use
tens of thousands of iterations.

```{r fit}
fit <- lodi(
  Y = sim$Y,
  K = 3,
  niter = 400,
  nburn = 200,
  thin  = 2,
  seed  = 1
)
```

## 3. Recovery of the shared-factor AR(1) coefficient

Truth is `rho = 0.7`:

```{r rho}
posterior_rho(fit)
```

## 4. Recovery of the within-time covariance

Element-wise RMSE between posterior mean and truth (Frobenius-style, over
the whole $J\times J$ matrix):

```{r sigma}
Sigma_hat  <- posterior_Sigma(fit, timepoint = 1)
Sigma_true <- sim$Sigma_true[, , 1]
sqrt(mean((Sigma_hat - Sigma_true)^2))
```

## 5. Full simulation

To reproduce the full Simulation 1 in the paper, increase to `N = 20`,
`T = 7`, `J = 50`, `niter = 30000`, `nburn = 15000`, `thin = 5` and repeat
over 10 seeds.
